Modeling the impacts of park access on health outcomes: a utility-based accessibility approach

### 2020-09-25 manuscript/submission/manuscript.tex
Update manuscript for reviewers

\usepackage{moreverb,url,natbib, multirow, tabularx}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
\renewcommand{\appendixname}{Supplementary Material}

@@

In a destination choice framework, the tracts represent the ``origins''
and the ``destinations'' are parks and green spaces in New York City. We
retrieved a polygons layer of public parks and green spaces within New
York City's municipal boundaries and checked it for accuracy and
relevance \citep{nycparks}. Upon inspection, we removed several
facilities that do not qualify as publicly accessible green space, such
as Yankee Stadium, Citi Field, and their surrounding parking lots. We
also removed parks of less than half an acre in size, as these appear to
be predominantly planted medians rather than legitimate public green
space. We consolidated individual geographic polygons comprising a
single facility --- as is the case in Flushing Meadows --- and
eliminated sub-facilities such as tennis courts or baseball fields
included within larger park facilities. Instead of these distinct
sub-facilities, we created variables for each containing park indicating
the presence of sports courts, playgrounds, and trails.

To this dataset of parks and regularized green spaces, we add a polygons
layer of cemeteries in New York that are open to the public. Cemeteries
are important green spaces that can be used for many types of physical
activity. These operations leave us with 1,277 distinct green spaces;
for simplicity we will refer to both parks and cemeteries as ``parks''
going forward. For each park, we calculate the size of the park in
acres.

@@

To determine which spatial effects specification was appropriate, we
estimated SLX and SDEM models of physical activity participation rates
as a function of tract covariates and accessibility. These two models
are presented in Table \ref{tab:slx-sdem}. With only a few exceptions,
the SLX and SDEM coefficient estimates for corresponding covariates lie
within the 95\% confidence intervals of the other model. A Hausman-style
test \citep{Pace2008} on the coefficients assumes a null hypothesis that
the coefficients are equivalent; this test produces \(p\)-value of only
\(1.307e-23\). Though this statistic is well beneath a common hypothesis
test threshold of \(\alpha = 0.05\), we elect to retain the null hypothesis
that the coefficients are equivalent, as the differences are at no point
practically different from each other. The consequences of rejecting the
null hypothesis in this case would be to suggest a model with spatial
dependence of the dependent variable; as stated above, we feel that such
a relationship is unreasonable. As a consequence of these analyses, we
adopt the SDEM specification moving forward as the spatial lag of the
errors is significant and the overall log likelihood of the SDEM is
higher than the SLX specification.

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} &
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Thu Jun  4 16:31:52 2020
 (Intercept) & -15.8424 & -26.8735 & -4.8112 &   & -24.9740 & -41.8930 & -8.0549 \\
  log(Density) & 0.0484 & -0.1314 & 0.2282 &   & 0.1775 & 0.0384 & 0.3166 \\
  log(Income) & 5.8210 & 5.2977 & 6.3443 &   & 5.9985 & 5.5746 & 6.4224 \\
  Fulltime & 0.1150 & 0.0936 & 0.1365 &   & 0.1275 & 0.1090 & 0.1460 \\
  College-educated & 0.0012 & -0.0272 & 0.0297 &   & 0.0076 & -0.0158 & 0.0309 \\
  Single Adults & -0.0433 & -0.0623 & -0.0244 &   & -0.0362 & -0.0526 & -0.0198 \\
  Youth (0-17) & -0.1511 & -0.1830 & -0.1192 &   & -0.1310 & -0.1576 & -0.1045 \\
  Young adults (18-34) & 0.0257 & 0.0008 & 0.0505 &   & 0.0295 & 0.0094 & 0.0496 \\
  Seniors (65+) & 0.0137 & -0.0185 & 0.0459 &   & 0.0403 & 0.0130 & 0.0677 \\
  Black population share & -0.0465 & -0.0584 & -0.0346 &   & -0.0499 & -0.0586 & -0.0411 \\
  Asian population share & -0.0686 & -0.0832 & -0.0541 &   & -0.0767 & -0.0873 & -0.0662 \\
  Hispanic population share & -0.1017 & -0.1140 & -0.0894 &   & -0.1025 & -0.1116 & -0.0934 \\
  Other Minorities & 0.0368 & -0.0643 & 0.1378 &   & 0.0037 & -0.0849 & 0.0923 \\
  $\gamma$: log(Density) & 1.2594 & 0.9413 & 1.5774 &   & 1.0985 & 0.7155 & 1.4815 \\
  $\gamma$: log(Income) & 2.3930 & 1.5476 & 3.2383 &   & 1.9742 & 0.9465 & 3.0020 \\
  $\gamma$: Fulltime & -0.1398 & -0.1804 & -0.0991 &   & -0.0397 & -0.0869 & 0.0076 \\
  $\gamma$: College-educated & -0.1312 & -0.1806 & -0.0818 &   & -0.0710 & -0.1305 & -0.0115 \\
  $\gamma$: Single Adults & -0.0480 & -0.0821 & -0.0140 &   & -0.0082 & -0.0504 & 0.0339 \\
  $\gamma$: Youth (0-17) & -0.1031 & -0.1618 & -0.0445 &   & -0.0108 & -0.0798 & 0.0583 \\
  $\gamma$: Young adults (18-34) & 0.1191 & 0.0762 & 0.1619 &   & 0.0842 & 0.0335 & 0.1349 \\
  $\gamma$: Seniors (65+) & 0.0108 & -0.0479 & 0.0695 &   & 0.0590 & -0.0102 & 0.1282 \\
  $\gamma$: Black population share & 0.0096 & -0.0054 & 0.0247 &   & 0.0010 & -0.0151 & 0.0172 \\
  $\gamma$: Asian population share & -0.0661 & -0.0840 & -0.0483 &   & -0.0397 & -0.0583 & -0.0210 \\
  $\gamma$: Hispanic population share & -0.0060 & -0.0216 & 0.0097 &   & -0.0010 & -0.0182 & 0.0162 \\
  $\gamma$: Other Minorities & 0.1868 & -0.0508 & 0.4244 &   & 0.0726 & -0.1845 & 0.3297 \\
  Accessibility & 0.5430 & 0.4195 & 0.6666 &   & 0.1663 & 0.0277 & 0.3048 \\
  $\lambda$: spatial correlation &  &  &  &   & 0.6905 & 0.6513 & 0.7296 \\

\midrule
Log Likelihood & \multicolumn{3}{c}{$-4831.974$} & & \multicolumn{3}{c}{$-4435.507$}\\
Num.Obs.       & \multicolumn{3}{c}{$2099$}   & & \multicolumn{3}{c}{$2099$}\\
\bottomrule
\end{tabular}
\end{table*}

The coefficients in the SDEM model are of two general types: the direct
effect resulting from a tract's own attributes and the indirect effect
(\(\boldsymbol{\gamma}\)) resulting from the spatially-weighted
attributes of its neighbors. For example, a percentage point increase in
the share of young adults in a tract increases the expected physical
activity rate in a tract by 0.02947 percentage points, and a percentage
point increase in the share of young adults \emph{in neighboring tracts}
increases the expected physical activity rate by an \emph{additional}
0.08417 percentage points. This opportunity to examine spatial
spillovers of attributes is a key benefit of using a spatial model.

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and
accessibility coefficients for three models using different
specifications of the utility equation, as well as the ten-minute walk
buffer calculated by ParkScore. Note that the model called ``Size and
Distance'' is precisely the model labeled ``SDEM'' in Table
\ref{tab:slx-sdem}. The controlling covariates are suppressed for
clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in Table \ref{tab:pa-fullmodels}. Each of the
three utility-based specifications is significant at the
\(\alpha = 0.05\) level or lower, and is of the hypothesized
directionality. That is, residents living in tracts with increased
utility-based accessibility to green spaces show a significantly higher
physical activity participation rate. Taking the rough mean of the 2
estimated utility-based coefficients, moving from the least-accessible
tract (\(A_i = -3\)) to the most-accessible tract (\(A_i = 3\)) is
expected to raise the physical activity rate by 0.9 percentage points.
With the understanding of the full 95\% confidence interval, we could
suggest that the true effect of excellent versus poor park access is
anywhere between 0.06 and 1.8 percentage points.

The 10-minute walk buffer is considerably less useful at isolating the
effects of park ``access'' on physical activity rates. As so few tracts
are located outside of the buffer, the standard error of the estimated
effect is large and implies an effect on activity rates anywhere from a
loss of 1.08 percentage points to a gain of 8.1.

@@

\begin{tabular}{l c c c }
\toprule
 & Size and Distance & Amenities & 10-Minute Walk \\
\midrule
Accessibility  & $0.1663^{*}$        & $0.1493^{*}$        & $0.5865$             \\
               & $[0.0277;\ 0.3048]$ & $[0.0073;\ 0.2914]$ & $[-0.1778;\ 1.3508]$ \\
\midrule
Num. obs.      & 2099                & 2099                & 2099                 \\
Parameters     & 28                  & 28                  & 28                   \\
Log Likelihood & -4435.3869          & -4436.0034          & -4436.9264           \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{$^*$ 0 outside the confidence interval 95\% confidence interval in brackets.  $y = $ tract-level physical activity rate.}}
\end{tabular}
\end{table*}

We now consider the impacts of a model where the dependent variable is
the \emph{obesity} rate in a tract, and physical activity becomes an
independent covariate alongside the controlling variables and the
accessibility metrics. Table \ref{tab:obesity-models} presents estimates
of the effect of all three utility-based accessibility measures as well
as the 10-minute walk buffer. As before, the estimates of the other
variables are available in Table \ref{tab:ob-fullmodel} in the Supplementary Material. The correlation between
physical activity rates and obesity is clear; for every percentage point
increase in physical activity rate, the expected obesity rate drops by
\(0.43\) percentage points in all four accessibility specifications. The
indirect effect of physical activity rates on obesity in neighboring
zones is inconsequential, supporting our methodological assertion that
public health variables are not spatially dependent, though the factors
leading to them may be.

@@

We readily acknowledge limitations in this study. As in any study
conducted with areal data, we are at risk of falling victim to the
ecological inference fallacy, where aggregate statistics mask or
contradict disaggregated or individual-level trends. \textcolor{blue}{The socioeconomic
and public health data used in this study are only available at the
tract level; projecting the tract-level data to the block group level
and computing more spatially precise accessibility logsums proved
infeasible as the spatial lags of the independent variables introduced
substantial collinearity in the model equations.} A large-sample survey
of individuals in New York City, including measured physical activities
and obesity would always be preferable to the tract-level data used in
this study. An ideal survey to address the question would incorporate
both sets of questions: physical activity and health data on one hand
and park use (including which parks were used and how frequently) on the
other. As no such dataset exists to our knowledge, this tract-level
aggregate analysis with asserted and transferred utility coefficients is
the possibility that remains.

This paper applies a previously-presented but little-used accessibility
statistic that could, in theory, accommodate many attributes of the
destination parks as well as the people who might use them. As an
illustration: the park-going population could be separated into at least
four delineated clusters, each preferring different amenities of a park:

@@

An analyst could then compute the utility-based accessibility for each
cluster with different utility values for each park's amenities, and
obtain a measure of a neighborhood's accessibility to park features that
its residents most care about. In this paper, we proceed only
incrementally towards this by adding some selected park amenities as an
element of each park's attractiveness above and beyond its size. \textcolor{blue}{The set
of amenities we included in the utility calculation --- and the
contribution of each amenity to the overall utility --- was dictated by
the availability of data on the park amenities in New York City and our
ability to find comparable prior studies with transferrable utility
parameters. We can envision a study where mobile device data revealing
the home locations of park users would be paired with more detailed park
amenities and use data (e.g.~geolocated Twitter data \emph{a la}
\citet{roberts2017using}) to estimate the utility contribution of these
features.} This could in turn provide a more nuanced understanding of the
relationship between park accessibility, \textcolor{blue}{use,} and health outcomes.

As a travel impedance measure, we used the Euclidean distance between
each tract's population-weighted centroid and the nearest point on the
edge of a park's border. Euclidean distances have well-rehearsed
limitations regarding their fidelity with the underlying infrastructure
network, etc. Network-based distances can also suffer from challenges
when applied to multimodal problems; these challenges are exacerbated
when the non-highway mode share is high, as is likely when considering
access to parks. \textcolor{blue}{We examined replacing the Euclidean distance with a
network-based distance; the choice of distance metric appeared
inconsequential to our larger findings in this case while substantially
increasing the computational load required. Additionally, we could not
verify the accuracy of the underlying network data at the scale of this
analysis. We therefore retain the Euclidean distance for simplicity.} A
better metric of travel impedance may be a mode choice model logsum,
which weights all alternative travel alternatives against each other. We
leave this as a recommendation for future research.

We compared our utility-based accessibility to a well-constructed
isochrone that has attracted attention in the literature. That said,
virtually all tracts in New York City are within this specific
isochrone. It is possible that this isochrone may be more discriminating
of park access in other cities, or that a different definition would
yield different results in New York City. This observation however
reinforces our suggestion that a measure explicitly based in the utility
of access is warranted.

Finally, this study is primarily focused on the hypothesis that
accessibility to parks encourages physical activity, which in turn
reduces obesity. There are a multitude of other hypotheses that might be
proposed and tested with the basic methodology we have employed here, or
competing explanations for the outcomes we have observed. It is
distinctly possible, for instance, that individuals who wish to exercise
regularly in parks choose to live near them. Given that the CDC models
informing the small-area obesity and physical activity estimates
presumably include variables likely to influence such preferences
(income, etc.), our investigation cannot isolate the preferences from
the effect. Controlling for such a self-selection effect would be
necessary to isolate the exogenous impacts of park access on obesity or
other health outcomes. And regarding these other variables: this study
did not consider potential relationships between park access and
hospitalization rates, life expectancy, respiratory disease, mental
health, or any number of potential beneficial outcomes hypothesized or
explored in the existing literature. \textcolor{blue}{The COVID-19 pandemic and its
associated social distancing behaviors in many regions of the world has
also drawn attention to problems of park access, use, and equity.}
Exploring these connections and their underlying mechanisms should be a
priority as city planners and urban architects attempt to improve the
quality of life of urban residents in the future.

@@

Increased physical activity and decreased obesity rates are critical
measures of improvement in public health. Although many have theorized
the link between park accessibility and these metrics, previous
literature has produced mixed findings, perhaps owing to the range of
variables modeled and the coarse spatial scale of the analyses. Using
New York City as a case study, we presented a holistic and flexible
measurement for park accessibility that compares the continuous distance
to all parks in the region, weighted against the size of the park and
its other amenities, with weights determinable through revealed
preferences. In terms of physical activity, we found a positive
relationship where the least park-accessible tracts have an expected
physical activity participation rate between 0.06 and 1.8 percentage
points lower than the most accessible tracts. We also found a suggestive
though not significant relationship between park accessibility and
expected obesity rates \emph{in addition to} the effect of physical
activity participation.

In both cases a common, isochrone-based analysis estimated a
statistically weak relationship with greater uncertainty. Isochrone
analyses are relatively common in the literature, perhaps because of the
widespread availability of and training in GIS software. In spite of
their widespread use, isochrones are relatively limited in terms of both
their theoretical underpinnings and their flexibility to accommodate
attributes of parks beyond their proximity. And even proximity may not
be adequately handled, as the isochrone threshold may be arbitrarily
asserted by the researcher. The model we apply in this paper extends a
more comprehensive and flexible approach for measuring the impact of
park access on health outcomes. Adopting utility-based accessibilities
of the kind used in this study will allow researchers to encompass the
full range of park amenities in their accessibility analyses, and to
separate the definition of access from the study of its effects. This
will in turn enhance the ability of planners to consider how multiple
attributes of a park --- from its location to its size to its amenities
and beyond --- benefit the health of the community the park serves.

@@

                                    & $ [ -0.0157;  0.0168]$ & $ [ -0.0151;  0.0172]$ & $ [ -0.0153;  0.0170]$ & $ [ -0.0157;  0.0168]$ \\
$\gamma$: Asian population share    & $-0.0410^{*}$          & $-0.0398^{*}$          & $-0.0401^{*}$          & $-0.0409^{*}$          \\
                                    & $ [ -0.0597; -0.0223]$ & $ [ -0.0584; -0.0212]$ & $ [ -0.0587; -0.0215]$ & $ [ -0.0596; -0.0222]$ \\
$\gamma$: Hispanic population share & $0.0009$               & $-0.0009$              & $-0.0008$              & $0.0008$               \\
                                    & $ [ -0.0164;  0.0182]$ & $ [ -0.0181;  0.0163]$ & $ [ -0.0181;  0.0164]$ & $ [ -0.0165;  0.0181]$ \\
$\gamma$: Other Minorities          & $0.0656$               & $0.0715$               & $0.0710$               & $0.0716$               \\
                                    & $ [ -0.1926;  0.3239]$ & $ [ -0.1856;  0.3287]$ & $ [ -0.1863;  0.3284]$ & $ [ -0.1866;  0.3299]$ \\
Accessibility                       &                        & $0.1610^{*}$           & $0.1472^{*}$           & $0.5865$               \\
                                    &                        & $ [  0.0238;  0.2982]$ & $ [  0.0058;  0.2886]$ & $ [ -0.1778;  1.3508]$ \\

>>>>

\usepackage{moreverb,url,natbib, multirow, tabularx}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

@@

In a destination choice framework, the tracts represent the ``origins''
and the ``destinations'' are parks and green spaces in New York City. We
retrieved a polygons layer of public parks and green spaces within New
York City's municipal boundaries and checked it for accuracy and
relevance \citep{nycparks}. Upon inspection, we removed several
facilities that do not qualify as publicly accessible green space, such
as Yankee Stadium, Citi Field, and their surrounding parking lots. We
also removed parks of less than half an acre in size, as these appear to
be predominantly planted medians rather than legitimate public green
space. We consolidated individual geographic polygons comprising a
single facility --- as is the case in Flushing Meadows --- and
eliminated sub-facilities such as tennis courts or baseball fields
included within larger park facilities. Instead of these distinct
sub-facilities, we created variables for each containing park indicating
the presence of sports courts, playgrounds, and trails. These operations
leave us with 1,191 distinct green spaces; For each park, we calculate
the size of the park in acres.

@@

To determine which spatial effects specification was appropriate, we
estimated SLX and SDEM models of physical activity participation rates
as a function of tract covariates and accessibility. These two models
are presented in Table \ref{tab:slx-sdem}. With only a few exceptions,
the SLX and SDEM coefficient estimates for corresponding covariates lie
within the 95\% confidence intervals of the other model. A Hausman-style
test \citep{Pace2008} on the coefficients assumes a null hypothesis that
the coefficients are equivalent; this test produces \(p\)-value of only
\(1.318e-23\). Though this statistic is well beneath a common hypothesis
test threshold of \(\alpha = 0.05\), we elect to retain the null
hypothesis that the coefficients are equivalent, as the differences are
at no point practically different from each other. The consequences of
rejecting the null hypothesis in this case would be to suggest a model
with spatial dependence of the dependent variable; as stated above, we
feel that such a relationship is unreasonable. As a consequence of these
analyses, we adopt the SDEM specification moving forward as the spatial
lag of the errors is significant and the overall log likelihood of the
SDEM is higher than the SLX specification.

\begin{table*}
\caption{Comparison of SLX and SDEM Coefficients}
\label{tab:slx-sdem}
\begin{tabular}{l d{2.4} d{2.4} d{2.4} c d{2.4} d{2.4} d{2.4} }
\toprule
 & \multicolumn{3}{c}{SLX} & & \multicolumn{3}{c}{SDEM} \\
\cmidrule{2-4}\cmidrule{6-8}
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.} & 
 & \multicolumn{1}{c}{Estimate} & \multicolumn{2}{c}{95\% Conf.Int.}\\
\midrule
% latex table generated in R 4.0.0 by xtable 1.8-4 package
% Thu Sep 24 13:41:03 2020
 (Intercept) & -15.8791 & -26.8066 & -4.9515 &   & -24.7352 & -41.5391 & -7.9312 \\ 
  log(Density) & 0.0502 & -0.1280 & 0.2284 &   & 0.1760 & 0.0371 & 0.3150 \\ 
  log(Income) & 5.8667 & 5.3476 & 6.3859 &   & 6.0134 & 5.5901 & 6.4368 \\ 
  Fulltime & 0.1157 & 0.0944 & 0.1369 &   & 0.1271 & 0.1086 & 0.1455 \\ 
  College-educated & 0.0029 & -0.0253 & 0.0311 &   & 0.0077 & -0.0156 & 0.0310 \\ 
  Single Adults & -0.0435 & -0.0623 & -0.0247 &   & -0.0365 & -0.0528 & -0.0201 \\ 
  Youth (0-17) & -0.1528 & -0.1844 & -0.1211 &   & -0.1320 & -0.1585 & -0.1055 \\ 
  Young adults (18-34) & 0.0245 & -0.0001 & 0.0492 &   & 0.0292 & 0.0092 & 0.0493 \\ 
  Seniors (65+) & 0.0108 & -0.0212 & 0.0427 &   & 0.0386 & 0.0112 & 0.0659 \\ 
  Black population share & -0.0471 & -0.0589 & -0.0353 &   & -0.0499 & -0.0586 & -0.0412 \\ 
  Asian population share & -0.0684 & -0.0828 & -0.0540 &   & -0.0764 & -0.0870 & -0.0659 \\ 
  Hispanic population share & -0.1003 & -0.1126 & -0.0881 &   & -0.1023 & -0.1114 & -0.0932 \\ 
  Other Minorities & 0.0341 & -0.0661 & 0.1343 &   & 0.0047 & -0.0837 & 0.0931 \\ 
  $\gamma$: log(Density) & 1.2513 & 0.9367 & 1.5659 &   & 1.0873 & 0.7062 & 1.4684 \\ 
  $\gamma$: log(Income) & 2.3641 & 1.5266 & 3.2016 &   & 1.9780 & 0.9563 & 2.9997 \\ 
  $\gamma$: Fulltime & -0.1346 & -0.1749 & -0.0943 &   & -0.0411 & -0.0882 & 0.0059 \\ 
  $\gamma$: College-educated & -0.1201 & -0.1692 & -0.0711 &   & -0.0704 & -0.1296 & -0.0112 \\ 
  $\gamma$: Single Adults & -0.0520 & -0.0857 & -0.0183 &   & -0.0094 & -0.0514 & 0.0325 \\ 
  $\gamma$: Youth (0-17) & -0.1013 & -0.1594 & -0.0432 &   & -0.0128 & -0.0815 & 0.0559 \\ 
  $\gamma$: Young adults (18-34) & 0.1131 & 0.0706 & 0.1555 &   & 0.0838 & 0.0334 & 0.1342 \\ 
  $\gamma$: Seniors (65+) & 0.0015 & -0.0568 & 0.0598 &   & 0.0545 & -0.0145 & 0.1235 \\ 
  $\gamma$: Black population share & 0.0099 & -0.0051 & 0.0248 &   & 0.0011 & -0.0149 & 0.0172 \\ 
  $\gamma$: Asian population share & -0.0644 & -0.0821 & -0.0467 &   & -0.0397 & -0.0582 & -0.0212 \\ 
  $\gamma$: Hispanic population share & -0.0074 & -0.0229 & 0.0081 &   & -0.0015 & -0.0185 & 0.0156 \\ 
  $\gamma$: Other Minorities & 0.1629 & -0.0725 & 0.3983 &   & 0.0723 & -0.1840 & 0.3286 \\ 
  Accessibility & 0.6575 & 0.5348 & 0.7801 &   & 0.2306 & 0.0907 & 0.3705 \\ 
  $\lambda$: spatial correlation &  &  &  &   & 0.6854 & 0.6459 & 0.7249 \\

\midrule
Log Likelihood & \multicolumn{3}{c}{$-4,815$} & & \multicolumn{3}{c}{$-4,433$}\\
Num.Obs.       & \multicolumn{3}{c}{$2,099$}   & & \multicolumn{3}{c}{$2,099$}\\
\bottomrule
\end{tabular}
\end{table*}

The coefficients in the SDEM model are of two general types: the direct
effect resulting from a tract's own attributes and the indirect effect
(\(\boldsymbol{\gamma}\)) resulting from the spatially-weighted
attributes of its neighbors. For example, a percentage point increase in
the share of young adults in a tract increases the expected physical
activity rate in a tract by 0.02922 percentage points, and a percentage
point increase in the share of young adults \emph{in neighboring tracts}
increases the expected physical activity rate by an \emph{additional}
0.08378 percentage points. This opportunity to examine spatial
spillovers of attributes is a key benefit of using a spatial model.

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and
accessibility coefficients for two models using different specifications
of the utility equation, as well as the ten-minute walk buffer
calculated by ParkScore. Note that the model called ``Size and
Distance'' is precisely the model labeled ``SDEM'' in Table
\ref{tab:slx-sdem}. The controlling covariates are suppressed for
clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in Table \ref{tab:pa-fullmodels}
of the Supplementary Material. Each of the two utility-based
specifications is significant at the \(\alpha = 0.05\) level or lower,
and is of the hypothesized direction That is, residents living in tracts
with increased utility-based accessibility to green spaces show a
significantly higher physical activity participation rate. Taking the
rough mean of the two estimated utility-based coefficients, moving from
the least-accessible tract (\(A_i = -3\)) to the most-accessible tract
(\(A_i = 3\)) is expected to raise the physical activity rate by 1.32
percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor
park access is anywhere between 0.3 and 2.1 percentage points.

In contrast, 10-minute walk buffer is considerably less useful at
isolating the effects of park ``access'' on physical activity rates. As
so few tracts are located outside of the buffer, the standard error of
the estimated effect is large and implies an effect on activity rates
anywhere from a loss of 0.18 percentage points to a gain of 1.35.

@@

\begin{tabular}{l c c c}
\toprule
 & Size and Distance & Amenities & 10-Minute Walk \\
\midrule
Accessibility  & $0.2306^{*}$        & $0.1923^{*}$        & $0.5865$             \\
               & $ [0.0907; 0.3705]$ & $ [0.0498; 0.3347]$ & $ [-0.1778; 1.3508]$ \\
\midrule
Num. obs.      & $2099$              & $2099$              & $2099$               \\
Parameters     & $28$                & $28$                & $28$                 \\
Log Likelihood & $-4433.0965$        & $-4434.7087$        & $-4436.9264$         \\
\bottomrule
\multicolumn{4}{l}{\scriptsize{$^*$ Null hypothesis value outside the confidence interval. 95\% confidence interval in brackets.  $y = $ tract-level physical activity rate.}}
\end{tabular}
\end{table*}

We now consider the impacts of a model where the dependent variable is
the \emph{obesity} rate in a tract, and physical activity becomes an
independent covariate alongside the controlling variables and the
accessibility metrics. Table \ref{tab:obesity-models} presents estimates
of the effect of all three utility-based accessibility measures as well
as the 10-minute walk buffer. As before, the estimates of the other
variables are available in Table \ref{tab:ob-fullmodels} of the
Supplementary Material. The correlation between physical activity rates
and obesity is clear; for every percentage point increase in physical
activity rate, the expected obesity rate drops by \(0.43\) percentage
points in all four accessibility specifications. The indirect effect of
physical activity rates on obesity in neighboring zones is
inconsequential, supporting our methodological assertion that public
health variables are not spatially dependent, though the factors leading
to them may be.

@@

We readily acknowledge limitations in this study. As in any study
conducted with areal data, we are at risk of falling victim to the
ecological inference fallacy, where aggregate statistics mask or
contradict disaggregated or individual-level trends. The socioeconomic
and public health data used in this study are only available at the
tract level; projecting the tract-level data to the block group level
and computing more spatially precise accessibility logsums proved
infeasible as the spatial lags of the independent variables introduced
substantial collinearity in the model equations. A large-sample survey
of individuals in New York City, including measured physical activities
and obesity would always be preferable to the tract-level data used in
this study. An ideal survey to address the question would incorporate
both sets of questions: physical activity and health data on one hand
and park use (including which parks were used and how frequently) on the
other. As no such dataset exists to our knowledge, this tract-level
aggregate analysis with asserted and transferred utility coefficients is
the possibility that remains.

This paper applies a previously presented but seldom applied
accessibility statistic that could, in theory, accommodate many
attributes of the destination parks as well as the people who might use
them. As an illustration: the park-going population could be separated
into at least four delineated clusters, each preferring different
amenities of a park:

@@

An analyst could then compute the utility-based accessibility for each
cluster with different utility values for each park's amenities, and
obtain a measure of a neighborhood's accessibility to park features that
its residents most care about. The set of amenities we included in the
utility calculation --- and the contribution of each amenity to the
overall utility --- was dictated by the availability of open data on the
park amenities in New York City and our ability to find comparable prior
studies with transferable utility parameters. It is remarkable that our
two utility specifications --- one with size and distance, and one with
size and distance plus amenities --- result in such similar model
estimates. This may indicate that the utility is driven largely by size
and distance, or that the additional park amenities we included in the
utility specification are spatially distributed in a way that correlates
with the health outcomes. Either way, further analysis examining more
amenity variables is warranted. We can envision a study where mobile
device data revealing the home locations of park users would be paired
with more detailed park amenities and use data (e.g.~geolocated Twitter
data \emph{a la} \citet{roberts2017using}) to estimate the utility
contribution of these features. This could in turn provide a more
nuanced understanding of the relationship between park accessibility,
use, and health outcomes.

As a travel impedance measure, we used the Euclidean distance between
each tract's population-weighted centroid and the nearest point on the
edge of a park's border. Euclidean distances have well-rehearsed
limitations regarding their fidelity with the underlying infrastructure
network, etc. Network-based distances can also suffer from challenges
when applied to multimodal problems; these challenges are exacerbated
when the non-highway mode share is high, as is likely when considering
access to parks. We examined replacing the Euclidean distance with a
network-based distance; the choice of distance metric appeared
inconsequential to our larger findings in this case while substantially
increasing the computational load required. Additionally, we could not
verify the accuracy of the underlying network data at the scale of this
analysis. We therefore retain the Euclidean distance for simplicity. A
better metric of travel impedance may be a mode choice model logsum,
which weights all alternative travel alternatives against each other. We
leave this as a recommendation for future research.

We compared our utility-based accessibility to a well-constructed
isochrone that has attracted attention in the literature. That said,
virtually all tracts in New York City are within this specific
isochrone. It is possible that this isochrone may be more discriminating
of park access in other cities, or that a different definition would
yield different results in New York City. This observation however
reinforces our suggestion that a measure explicitly based in the utility
of access is warranted. We acknowledge that a utility-based framework
for access may be more technically difficult for some practitioners to
independently construct for their analyses than an isochrone or even a
gravity-based measure. That said, it may not be necessary for practicing
planners to construct this measure themselves: web-based tools such as
ParkIndex \citep{Kaczynski2016} and even WalkScore
(\url{https://www.walkscore.com}) abstract complex methodologies into
tools that planners can and do readily apply.

Finally, this study is primarily focused on the hypothesis that
accessibility to parks encourages physical activity, which in turn
reduces obesity. There are a multitude of other hypotheses that might be
proposed and tested with the basic methodology we have employed here, or
competing explanations for the outcomes we have observed. It is
distinctly possible, for instance, that individuals who wish to exercise
regularly in parks choose to live near them. Given that the CDC models
informing the small-area obesity and physical activity estimates
presumably include variables likely to influence such preferences
(income, etc.), our investigation cannot isolate the preferences from
the effect. Controlling for such a self-selection effect would be
necessary to isolate the exogenous impacts of park access on obesity or
other health outcomes. And regarding these other variables: this study
did not consider potential relationships between park access and
hospitalization rates, life expectancy, respiratory disease, mental
health, or any number of potential beneficial outcomes hypothesized or
explored in the existing literature. The COVID-19 pandemic and its
associated social distancing behaviors in many regions of the world has
also drawn attention to problems of park access, use, and equity.
Exploring these connections and their underlying mechanisms should be a
priority as city planners and urban architects attempt to improve the
quality of life of urban residents in the future.

@@

Increased physical activity and decreased obesity rates are critical
measures of improvement in public health. Although many have theorized
the link between park access and public health, previous literature has
produced mixed findings, perhaps owing to the wide range of
accessibility definitions. Using New York City as a case study, we
presented a holistic and flexible measurement for park accessibility
that compares the continuous distance to all parks in the region,
weighted against the size of the park and its other amenities, with
weights determinable through revealed preferences. In terms of physical
activity, we found a positive relationship where the least
park-accessible tracts have an expected physical activity participation
rate between 0.06 and 1.8 percentage points lower than the most
accessible tracts. We also found a suggestive though not significant
relationship between park accessibility and expected obesity rates
\emph{in addition to} the effect of physical activity participation.

In both cases a common, isochrone-based analysis estimated a
statistically weak relationship with greater uncertainty. Isochrone
analyses are relatively common in the literature, perhaps because of the
widespread availability of and training in GIS software. In spite of
their widespread use, isochrones are relatively limited in terms of both
their theoretical underpinnings and their flexibility to accommodate
attributes of parks beyond their proximity. And even proximity may not
be adequately handled, as the isochrone threshold may be arbitrarily
asserted by the researcher. The model we apply in this paper extends a
more comprehensive and flexible approach for measuring the impact of
park access on health outcomes.

Adopting utility-based accessibilities of the kind used in this study
will allow researchers to encompass the full range of park amenities in
their accessibility analyses, and to separate the definition of access
from the study of its effects. This will in turn enhance the ability of
planners to consider how multiple attributes of a park --- from its
location to its size to its amenities and beyond --- benefit the health
of the community the park serves.

@@

                                    & $ [ -0.0157;  0.0168]$ & $ [ -0.0149;  0.0172]$ & $ [ -0.0153;  0.0169]$ & $ [ -0.0157;  0.0168]$ \\
$\gamma$: Asian population share    & $-0.0410^{*}$          & $-0.0397^{*}$          & $-0.0401^{*}$          & $-0.0409^{*}$          \\
                                    & $ [ -0.0597; -0.0223]$ & $ [ -0.0582; -0.0212]$ & $ [ -0.0587; -0.0216]$ & $ [ -0.0596; -0.0222]$ \\
$\gamma$: Hispanic population share & $0.0009$               & $-0.0015$              & $-0.0012$              & $0.0008$               \\
                                    & $ [ -0.0164;  0.0182]$ & $ [ -0.0185;  0.0156]$ & $ [ -0.0184;  0.0159]$ & $ [ -0.0165;  0.0181]$ \\
$\gamma$: Other Minorities          & $0.0656$               & $0.0723$               & $0.0719$               & $0.0716$               \\
                                    & $ [ -0.1926;  0.3239]$ & $ [ -0.1840;  0.3286]$ & $ [ -0.1849;  0.3287]$ & $ [ -0.1866;  0.3299]$ \\
Accessibility                       &                        & $0.2306^{*}$           & $0.1923^{*}$           & $0.5865$               \\
                                    &                        & $ [  0.0907;  0.3705]$ & $ [  0.0498;  0.3347]$ & $ [ -0.1778;  1.3508]$ \\
$\lambda$: spatial correlation      & $0.6985^{*}$           & $0.6854^{*}$           & $0.6885^{*}$           & $0.6987^{*}$           \\
